An application of Graph Theory to MDAO problem formulation

### 2012-10-03 intro.tex
tweaking the intro some more

    An alternate matrix based syntax, called a Functional Dependency Table (FDT), was proposed by Michelena and Papalambros. 
    FDT represents the relationship between functions, including objectives and constraints, and specific variables that affect 
    them\cite{Michelena1997}. Similar to DSM, FDT also describes an adjacency matrix of a graph. Unlike the DSM graph, 
    however, the graph is undirected and nodes can represent analysis tools, objectives, 
    or constraints. Edges between nodes represent a dependence on the same 
    variable. Wagner and Papalambros made use of the FDT to solve a graph partitioning problem that yielded 
    more efficient optimization problem decompositions\cite{Wagner1993}. While FDT succeeds at capturing the 
    information about objectives and constraints, it neglects the data dependency captured by DSM. 
    [TODO: There is more recent research to cite here, like Allison's Work.]

    Lamb and Martins included the variables, objectives, and constraint functions as nodes in an Extended 
    DSM (XDSM) in order to capture a more complete problem formulation for MDAO problems\cite{Lambe2012}. By adding in those 
    elements, they partially combined a traditional DSM with an FDT. 
    This allows XDSM to represent data dependency between multiple analysis tools as well as between analysis tools and
    objective/constraint functions. With the additional information included in an XDSM Lu and Martins applied both ordering and partitioning 
    algorithms on an MDAO test problem named the Scalable Problem \cite{Lu2012}.

    Although XDSM captures part of the FDT formulation, it still leaves out the variables themselves. As a result, all variable information is aggregated 
    so that for the problem from Eqn. \ref{eqn:simple_fpf} you can say that $A$ depends on $B$ or vice versa, but you can't identify which 
    individual variables are interacting in the dependency cycle. Without the detailed variable information, you can't construct the compatibility 
    constraints necessary to implement the problem. Hence, to complete the DSM for use with a fundamental problem formulation you need 
    to add in nodes for each variable in the analysis. In the following sections we describe the necessary syntax for specifying a 
    problem formulation with DSM syntax and show how to make use of the resulting graph to find the FPF from any given graph.

>>>>

    An alternate matrix based syntax, called a Functional Dependency Table (FDT), was proposed by Michelena and Papalambros. 
    FDT represents the relationship between functions, including objectives and constraints, and specific variables that affect 
    them\cite{Michelena1997}. Similar to DSM, FDT also describes an adjacency matrix of a graph. Unlike the DSM graph, 
    however, the graph is undirected and nodes can represent analysis tools, objectives, 
    or constraints. Edges between nodes represent a dependence on the same 
    variable. Wagner and Papalambros made use of the FDT to solve a graph partitioning problem that yielded 
    more efficient optimization problem decompositions\cite{Wagner1993}. While FDT succeeds at capturing the 
    information about objectives and constraints, it neglects the data dependency captured by DSM. 
    [TODO: There is more recent research to cite here. e.g. Allison's Work.]

    [TODO: insert FDT of simple problem here]

    Lamb and Martins included the variables, objectives, and constraint functions as nodes in an Extended 
    DSM (XDSM) in order to capture a more complete description of solution strategies for MDAO problems\cite{Lambe2012}. By adding in those 
    elements, they partially combined a traditional DSM with an FDT. 
    This allows XDSM to represent data dependency between multiple analysis tools as well as between analysis tools and
    objective/constraint functions. With the additional information included in an XDSM Lu and Martins applied both ordering and partitioning 
    algorithms on an MDAO test problem named the Scalable Problem \cite{Lu2012}.

    [TODO: insert XDSM for simple problem solved with MDF here]

    Although XDSM captures part functional aspects of FDT, it  leaves out the variables themselves. As a result, all variable information is aggregated 
    so that for the problem from Eqn. \ref{eqn:simple_fpf} you can say that $A$ depends on $B$ or vice versa, but you can't identify which 
    individual variables are interacting in the dependency cycle. Without the detailed variable information, you can't construct the compatibility 
    constraints necessary to implement the problem. Additionally, XDSM requires the use of solver and optimizer blocks to represent 
    the relationship between design variables and objectives/constraints. By introducing solver or optimizer blocks XDSM automatically provides
    some kind of solution strategy. Hence XDSM is too specific for use with a fundamental problem formulation.

    By taking XDSM, removing the requirement for solver/optimizer nodes and adding in nodes for each variable we are able to fully describe 
    the problem formulation for a general MDAO problem. In the following sections we describe the necessary syntax for specifying a 
    problem formulation withing a DSM and show how to make use of the resulting graph to find the FPF from any given graph. For completeness we 
    also present algorithms for converting between the general DSM and the more specific formulations discussed above.
